|

### 2025-01-23 output/Letter_to_editor_reviewers.Rmd
Complete first draft of response to editor

@@

>>>>

We think the motivation and psychometric utility of our approach are more
related with the interpretation of the item parameters than with the latent
abilities.
To our understanding, the better interpretation of the item parameters that
results from our approach provides indeed a better insight into how the results
are used.
<!-- TODO: Complete -->

@@

<!-- TODO: Reply -->
